What's in a Domain? Anaylsis of URL Features

### 2022-09-30 paper/paper.tex
Reorganisation of CLI params and function names, bug fixes and documentation

\begin{table*}
\caption{URL Features}
\label{tab:features}
\begin{tabular}{|l|l|l|l|}
\toprule
Group         &Feature              &Type        &Definition  \\
\midrule
Protocol      &protocol\_name        &Category    &The exact protocol name    \\
              &protocol\_type        &Category    &Protocol categorised by purpose    \\
              &protocol\_exists      &Boolean     &Flag indicating presence of protocol   \\
\midrule
Host          &host\_is\_ip           &Boolean     &Flag indicating if the host is an IP address    \\
              &ext\_type             &Category    &TLD extension categorised by purpose    \\
              &ext\_freq             &Boolean     &TLD extension frequency in internet traffic   \\
\midrule
Path          &path\_depth           &Numeric     &The number of forward slashes    \\
              &path\_words           &Numeric     &Count of distinct words    \\
\midrule
File          &file\_ext             &Category    &The exact file extension e.g. "exe" or "php"    \\
              &file\_type            &Category    &File extension categorised by function \& purpose    \\
              &file\_ext\_exists      &Boolean     &Flag indicating presence of protocol   \\
\midrule
Params        &name                 &Category    &The exact protocol name    \\
              &type                 &Category    &Protocol categorised by purpose    \\
              &exists               &Boolean     &Flag indicating presence of protocol   \\
\bottomrule
\end{tabular}
\end{table*}

@@

The data used in this study was collected from a collction of publications that 
present internet classification problems containing URLs as a key, or sole feature.
The IS Malcious URL classification dataset contains both malware and phishing URLS 
that need to be discriminated against benign URLS\cite{Mamun2016}.
The world wide web knowledge base (WebKb) 4 Universities data set contains a wide
range of university URLs categorised into multiple topic categories\cite{Craven1998}.
These 3 URL classification problems are summarised in Table \ref{tab:data}

\begin{table}
\caption{Datasets}
\label{tab:data}
\begin{tabular}{|l|r|r|}
\toprule
Dataset        &Records        &Classes  \\
\midrule
Malware        &               &2        \\
Phishing       &               &2        \\
WebKb 4Uni     &               &7        \\
\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table*}
\caption{URL Features}
\label{tab:features}
\begin{tabular}{|l|l|l|l|}
\toprule
Group         &Feature              &Type        &Definition  \\
\midrule
Protocol      &protocol\_name         &Category    &The exact protocol name    \\
              &protocol\_type         &Category    &Protocol categorised by purpose    \\
              &protocol\_exists       &Boolean     &Flag indicating presence of protocol   \\
\midrule
Host          &host\_is\_ip           &Boolean     &Flag indicating if the host is an IP address    \\
              &host\_has\_port        &Boolean     &Flag indicating if a port number is explicitly specified    \\
              &domain\_sections       &Numeric     &Count of period separated domain sections    \\
              &domain\_reg\_year      &Numeric     &Year in which the domain was initially registered    \\
              &subdomain\_type        &Category    &Categorisation of the purpose of the subdomain \\
              &subdomain\_freq        &Numeric     &Frequency of the subdomain in internet traffics    \\
              &tld\_type              &Category    &TLD extension categorised by purpose    \\
              &tld\_freq              &Boolean     &TLD extension frequency in internet traffic   \\
\midrule
Path          &path\_depth            &Numeric     &The number of forward slashes    \\
              &path\_words            &Numeric     &Count of distinct words    \\
              &path\_has_date         &Boolean     &Flag indicating if a date is detected in the path  \\
              &path\_is_home          &Boolean     &Flag indicating if the path starts with a home directorys    \\
\midrule 
File          &file\_ext              &Category    &The exact file extension e.g. "exe" or "php"    \\
              &file\_type             &Category    &File extension categorised by function \& purpose    \\
              &file\_ext\_exists      &Boolean     &Flag indicating presence of protocol   \\
\midrule
Params        &params\_len            &Numeric     &The length of the parameter string    \\
              &params\_count          &Numeric     &The count of the key value pairs in the param string    \\
              &params\_has\_url       &Boolean     &Flag indicating presence of a raw URL within the parameter string   \\
              &params\_enc\_url       &Boolean     &Flag indicating presence of an encoded URL within the parameter string   \\
              &params\_enc\_char      &Boolean     &Flag indicating presence of an encoded character within the parameter string   \\
              &params\_frag\_len      &Numeric     &Length of a hash delineated fragement at the end of the parameter string   \\
\bottomrule
\end{tabular}
\end{table*}

@@

The data used in this study was collected from a collction of publications that 
present internet classification problems containing URLs as the primary feature.
The ISCX Malcious URL classification dataset contains both malware and phishing URLS 
that need to be discriminated against benign URLS\cite{Mamun2016}.
The world wide web knowledge base (WebKb) 4 Universities data set contains a wide
range of university URLs categorised into multiple topic categories\cite{Craven1998}.
These 3 URL classification problems are summarised in Table \ref{tab:data}

\begin{table}
\caption{Datasets}
\label{tab:data}
\begin{tabular}{|l|r|r|}
\toprule
Dataset        &Records        &Classes  \\
\midrule
Malware        &46,944          &2        \\
Phishing       &45,343          &2        \\
WebKb 4Uni     &8,284           &7        \\
\bottomrule
\end{tabular}
\end{table}

We generate all url features for each of these datasets and then apply a range of machine learning
techniques to build an appropriate classifier.
